\newglossaryentry{prodenv}
{
    name=production environment,
    description={The environment in which a software or product is acutally put into operation for its intended user base or audience. }
}

\newglossaryentry{devenv}
{
    name=development environment,
    description={The environment in which a software or product runs to be tested, or used for development of other software or products, before it is put into production.}
}

\newglossaryentry{backend}
{
    name=backend,
    description={Refers to the business logic and data handling, what the user does not see, in a computer system.}
}

\newglossaryentry{frontend}
{
    name=frontend,
    description={Refers to the presentation layer, what the user sees, in a computer system.}
}

\newglossaryentry{backlog}
{
    name=backlog,
    description={Refers to an accumulation, especially of unfinished work or unfilled orders.}
}

\newglossaryentry{SDK}
{
    name=Software Development Kit (SDK),
    description={A set of tools that are built to help develop applications for a specific platform or software framework.}
}

\newglossaryentry{mockup}
{
    name=Mockup,
    description={A layout of printed matter or digital content.}
}


\newglossaryentry{branch}
{
    name=Branch,
    description={A branch is a set of code changes that are separate from other code changes. These branches, that is code changes, can be merged together to become one set of code changes. }
}

\newglossaryentry{hallway test}
{
    name=Hallway test,
    description={Hallway testing is a quick, cheap method of usability testing in which randomly selected people are asked to try using the product or service.}
}

\newglossaryentry{guerrilla test}{
    name=Guerrilla testing,
    description={Approach unsuspecting test subject in their natural habitat, and make them perform a set of task while observing them.}
}