\begin{longtable}{|L{1cm}|L{1.5cm}|L{1.5cm}|L{1.5cm}|L{2cm}|L{4.5cm}|L{1.5cm}|} \\
\hline
\textbf{Age} & \textbf{Sex} & \textbf{Borrowing books from  company} & \textbf{Borrowing books from friends} & \textbf{Interested in sharing books with} & \textbf{Do you wish to limit the availability of the books you own? How? Why/Why not?} & \textbf{What line of work are you in?} \\ \hline
31-40 & Male & 1-3 times a year & 1-3 times a year & Colleagues, Friends, Family & No & Academia (teaching + research) \\ \hline
\textgreater 61 & Male & 1-3 times a year & 1-3 times a year & Colleagues, Friends, Family & There are books that i will not share with anybody since they cannot be replaced. & professor emeritus \\ \hline
31-40 & Male & Never & 1-3 times a year & Colleagues, Friends, Family & No. & Research \\ \hline
31-40 & Male & Never & 1-3 times a year & Friends of friends, Colleagues, Friends, Family &  & IT researcher \\ \hline
51-60 & Male & 1-3 times a year & 1-3 times a year & Colleagues, Friends, Family & Every book that I have refined and finetuned with margin notes and back cover pockets are too valuable for me to be lent out. Apprx. 50 \% of my books have margin notes & creator \\ \hline
21-30 & Female & 1-3 times a year & 1-3 times a year & Strangers, Colleagues, Friends, Family & Will mainly share academic literature with colleagues and fiction with friends, while travel books could be available for both. I guess  categorizing books by category would be useful? & Education / engineering \\ \hline
41-50 & Male & Less than once per week & 1-3 times a year & Colleagues, Friends, Family &  & Research \\ \hline
21-30 & Male & 1-3 times a year & 1-3 times a year & Colleagues, Friends &  & PhD student \\ \hline
51-60 & Female & Never & 1-3 times a year & Friends, Family & - share by category (e.g. work books with colleagues). - share only with trustable people (the ones who return the books they loan) & IT professor \\ \hline
21-30 & Female & Never & 1-3 times a year & Colleagues, Friends, Family &  & Academic administration \\ \hline
51-60 & Male & Less than once per week & 1-3 times a year & Colleagues, Friends, Family &  & Professor \\ \hline
41-50 & Male & More than once per week & 1-3 times a year & Colleagues, Friends, Family &  & Teaching \\ \hline
51-60 & Female & 1-3 times a year & 1-3 times a year & Friends, Family &  & Veileder offentlig sektor \\ \hline
21-30 & Male & Less than once per week & Less than once per week & Strangers, Friends of friends, Colleagues, Friends, Family &  & PhD student \\ \hline
31-40 & Male & Less than once per week & Less than once per week & Colleagues, Friends, Family &  & research \\ \hline
\textgreater 61 & Male & Less than once per week & Less than once per week & Colleagues & No limits, as long as I am not using - or soon will be using - the book myself & university professor \\ \hline
41-50 & Male & Less than once per week & Less than once per week & Friends of friends, Colleagues, Friends, Family &  & IT \\ \hline
41-50 & Male & Less than once per week & Less than once per week & Friends of friends, Colleagues, Friends &  & Professor \\ \hline
51-60 & Male & Less than once per week & Less than once per week & Colleagues, Friends, Family & - risk of books not being returned- risk of not having them available when I need them & professor \\ \hline
21-30 & Female & Never & Less than once per week & Friends of friends, Colleagues, Friends, Family &  & phd student \\ \hline
31-40 & Female & 1-3 times a year & Less than once per week & Colleagues, Friends, Family & Not at all - I think papers/magazines should be shared rather than kept away. & researcher \\ \hline
51-60 & Male & Less than once per week & Less than once per week & Family &  & teachers \\ \hline
21-30 & Male & Never & Never & Friends of friends, Colleagues, Friends, Family & Maybe just how long they can borrow it. Otherwise, no. &  \\ \hline
21-30 & Female & Never & Never & Colleagues, Friends, Family &  &  \\ \hline
41-50 & Male & Less than once per week & Never & Colleagues & i use kindle. it has thousands of books. however, i have also hundreds of work related books in my own office. nobody reads them. it would be nice if my books would become valuable for my colleagues. now the books are just staying in my office self for no good reason. i would want to try to use your app with my colleagues. & professor \\ \hline
41-50 & Female & Never & Never & Friends & Easier to get them back from friends than from a "stranger"? & adm \\ \hline
21-30 & Female & Never & Never & Nobody & I would limit the availability of my books to my closest colleagues and boss/supervisor because I need most of them for work. I also tend to write many comments, to underline and highlight a lot, so sharing wouldn't be a viable option. & researcher \\ \hline
41-50 & Female & Less than once per week & Never & Strangers, Colleagues, Friends & From my point of view there is no need to limit the availability of the books. It would be nice to see what kind of professional books my colleagues have because sometimes it's hard to find a one available in library. & Project manager \\ \hline
31-40 & Male & Never & Never & Friends, Family &  & researcher \\ \hline
21-30 & Male & 1-3 times a year & Once per week & Friends of friends, Colleagues, Friends & Easy to borrow in the work as it's easy to get it back when needed. I'd better know the person well before borrowing it across campuses. & research fellow \\ \hline
31-40 & Male & 1-3 times a year & Less than once per week & Strangers &  & researcher \\ \hline

\end{longtable}