\begin{sidewaystable}[]
\centering
\begin{tabular}{|L{3cm}|C{1cm}|C{1cm}|C{.75cm}|L{6cm}|L{9cm}|}
\hline
\textbf{Description} & \textbf{\begin{tabular}[c]{@{}c@{}}P.\\ (1-10)\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}C.\\ (1-10)\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Risk \\ value\end{tabular}} & \textbf{Prevention} & \textbf{Solution} \\ \hline
Task not completed & 4 & 6 & 24 & Ensure estimates are adequate, and allocate sufficient resources for tasks & Work extra hours to complete the task \\ \hline
Absence (+4 days) & 4 & 5 & 20 & If a group member is going away it must be notified in advance & If we know that a group member is leaving we can assign tasks that can be done \\ \hline
Can not solve a problem & 5 & 4 & 20 & Good internal communication in the team will prevent most problems & Consult advisors, customer or course staff \\ \hline
Loss of data & 3 & 6 & 18 & Use version control and online backups for all documents and resources & Restore backup.  \\ \hline
Computer malfunction & 2 & 8 & 16 & Keep software updated. & Try to find a new computer for the team member \\ \hline
No feedback from users & 2 & 8 & 16 & Try to reach users through multiple channels like the customer, Reddit, Facebook and more & Contact family and friends \\ \hline
Conference room unavailable & 5 & 3 & 15 & Book rooms in advance & Find a quiet spot and conduct the meeting on a laptop \\ \hline
Missing competence & 5 & 3 & 15 & Map team members competence and preferred technologies & Find alternative solutions if possible. If not, allocate resources for team member to learn the new technology \\ \hline
Illness & 7 & 2 & 14 & Try to prevent taking unnecessary health risks. & Divide the team members task among the team members \\ \hline
Latecomers & 7 & 2 & 14 & Make sure all team members know when meetings will take place through calendars and messages & The latecomer will have to work additional hours to make up for lost time. The team member should also communicate its status by other means if possible \\ \hline
Miscommunication & 2 & 6 & 12 & Clearly define all tasks and who is responsible for their execution & Find out what has been done and reorganize. \\ \hline
Apple disapproves the app & 2 & 6 & 12 & Make sure not to use private APIs and follow Apples guide lines & Update what is preventing the app from being approved and submit for review \\ \hline
Loss of team member & 1 & 9 & 9 & Make sure all team members feel included and are in good health & Distribute the late team members tasks among the remaining team members. Revise the project plan and remove the least important tasks if necessary \\ \hline
Force majeure & 1 & 7 & 7 & Good communication & Work individually and arrange meetings when possible \\ \hline
Unreachable version control server & 1 & 5 & 5 & Store versions locally to be able to keep working. & Keep editing local revisions and push when the service is back online. Communicate to avoid redundancy and conflicts \\ \hline
\end{tabular}
\caption{Risk assessment}
\label{table:risk-assessment}
\end{sidewaystable}